Red bus, blue bus; and the choice between Florida, California, and Florida plus a nickel

### 2025-02-11 inst/red_bus_blue_bus.Rmd

@@

The red bus-blue bus problem was originally stated by @chipman1960 and
discussed by @davidson1970 and @alvo2010 (page 153).
Debussy-Beethoven was @debreu1960.  I have lost the original reference
to the Holiday problem.

>>>>

To cite the `hyper2` package in publications, please use
@hankin2017_rmd.

@@

The red bus-blue bus problem was originally stated by @chipman1960 and
discussed by @davidson1970 and @alvo2014 (page 153).
Debussy-Beethoven was @debreu1960.  The Holiday problem is discussed
in @tverskey1972 (in the form of trips to Paris or Rome), attributed
to "L. J. Savage"; in this document I use Florida and California,
which I did not make up, but cannot find the original reference.
